### 2010-07-30 Thesis/Chapter3.tex
- Update 30 July - Changed outline according to what we discussed with Stephane + increased level of details + bib updated + creation of chapter 3
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@138 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\part{Introduction}

	\chapter{Medical simulation}
		\section{General context and goal: medical training, patient-specific planning and per-operative guidance}
		\section{Challenges (trade-off between accuracy and real-time)}

%	\chapter{One key point in medical simulation: soft-tissue modelling}
%		\section{Necessary background in continuum mechanics}
%			\subsection{Deformation tensor and strain tensor}
%			\subsection{Stress and constitutive laws}
%		\section{Tissue characterisation}
%			\subsection{Material models for organs (non-linear, visco-elastic and anisotropic)}
%			\subsection{Measure/estimation of model parameters?}
	\input{chapter2}

	\chapter{Main principles of Finite Element Method (or how to solve equations of continuum mechanics from previous section)}
		\section{Discretisation}
		\section{Derivation of element equations}
		\section{Assembly of element equations}
		\section{Solution of global problem}

\part{Solid organs modelling}

	\chapter{State of art: FEM}

	\chapter{Linear not accurate => Non-linear FEM => Introduction of TLED}
		\section{Differences with classic FEM and reasons of its efficiency}
		\section{Visco-elasticity and anisotropy added \OC{MICCAI 2008; MedIA 2009}}

	\chapter{GPU implementation of TLED}
		\section{What is GPGPU}
		\section{Re-formulation of the algorithm for its Cg implementation}
		\section{CUDA implementation/optimisations \OC{ISBMS 2008a}}

	\chapter{Implementation in SOFA}
		\section{Presentation of SOFA project and architecture}
		\section{Implementation in SOFA and TLED released in open-source}

\part{Hollow organs modelling}

	\chapter{State of art: hollow structures}
		\section{Non-physic approaches (computer graphics stuff)}
		\section{Physically accurate approches (plates/shells)}

	\chapter{Why a shell FEM? Colonoscopy simulator project}
		\section{Project introduction}
		\section{Mass-spring model for colon implemented on GPU \OC{ISBMS 2008b}}

	\chapter{More accurate: a co-rotational triangular shell model \OC{ISBMS 2010}}
		\section{Model description}
		\section{Validation}
		\section{Application to implant deployment simulation in cataract surgery}

	\chapter{'Shell meshing' technique \OC{MICCAI 2010}}
		\section{State of art: reconstruction/simplification}
		\section{Our method}

	\chapter{Applications to medical simulation}
		\section{Nice medical stuff to show}
		\section{Interaction solid/hollow organs}

\part{Conclusion}

>>>>

\chapter{Main principles of Finite Element Method (most used technique to solve equations of continuum mechanics)}
\label{chap3}
\begin{shortAbstract}
Blabla
\end{shortAbstract}

\section{Introduction}

\section{Discretisation}

\section{Derivation of element equations}

\section{Assembly of element equations}

\section{Solution of global problem}

### 2010-07-30 Thesis/outline.tex
Update 15 July - Started chapter "soft-tissue modelling"
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@129 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
- Update 30 July - Changed outline according to what we discussed with Stephane + increased level of details + bib updated + creation of chapter 3
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@138 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

	\chapter{Medical simulation}
		\section{General context and goal: medical training, patient-specific planning and per-operative guidance}
		\section{Challenges (trade-off between accuracy and real-time)}

	\chapter{One key point in medical simulation: soft-tissue modelling}
		\section{Necessary background in continuum mechanics}
			\subsection{Deformation tensor and strain tensor}
			\subsection{Stress and constitutive laws}
		\section{Tissue characterisation}
			\subsection{Material models for organs (non-linear, visco-elastic and anisotropic)}
			\subsection{Measure/estimation of model parameters}

	\chapter{Main principles of Finite Element Method (or how to solve equations of continuum mechanics from previous section)}
		\section{Discretisation}
		\section{Derivation of element equations}
		\section{Assembly of element equations}
		\section{Solution of global problem}

@@

	\chapter{State of art: FEM}

	\chapter{Linear not accurate => Non-linear FEM => Introduction of TLED}
		\section{Differences with classic FEM and reasons of its efficiency}
		\section{Visco-elasticity and anisotropy added \OC{MICCAI 2008; MedIA 2009}}

	\chapter{GPU implementation of TLED}
		\section{What is GPGPU}
		\section{Re-formulation of the algorithm for its Cg implementation}
		\section{CUDA implementation/optimisations \OC{ISBMS 2008a}}

	\chapter{Implementation in SOFA}
		\section{Presentation of SOFA project and architecture}
		\section{Implementation in SOFA and TLED released in open-source}

@@

	\chapter{State of art: hollow structures}
		\section{Non-physic approaches (computer graphics stuff)}
		\section{Physically accurate approches (plates/shells)}

	\chapter{Colonoscopy simulator project}
		\section{Project introduction}
		\section{Mass-spring model for colon implemented on GPU \OC{ISBMS 2008b}}

	\chapter{More accurate: a co-rotational triangular shell model \OC{ISBMS 2010}}
		\section{Model description}
		\section{Validation}
		\section{Application to implant deployment simulation in cataract surgery}

@@

	\chapter{Applications to medical simulation}
		\section{Nice medical stuff to show}
		\section{Interaction solid/hollow organs}

\part{Conclusion}

>>>>

	\chapter{Medical simulation}
		\section{General context}
			\subsection{Simulators for everything: we started by simulating what is simple}
			\subsection{As complexity increases, applications to medical training, patient-specific planning and per-operative guidance}
		\section{Challenges}					
			\subsection{Photorealistic rendering}
			\subsection{Accurate haptic feedback}
			\subsection{Physically realist organ modelling in real-time}

	\input{chapter2}

	\input{chapter3}

@@

	\chapter{State of art: FEM}
		\section{Expose the problem: how to model solid organs?}
		\section{Techniques using geometrical kind of approaches}
			\subsection{Shape matching}
		\section{Techniques relying on physics}
			\subsection{Mass-spring}
		\section{Techniques based on continuum mechanics}	
			\subsection{FEM with mesh (highlight evolution: linear, topological changes, co-rotational, non-linear, GPU)}
			\subsection{Meshless (supposedly good for handling topological changes but other issues}

	\chapter{Introduction of TLED}
		\section{Description of the algorithm (neo-Hookean, explicit integration, independent elements, parallelisable on GPU)}
		\section{Visco-elasticity and anisotropy added \OC{MICCAI 2008; MedIA 2009}}

	\chapter{GPU implementation of TLED}
		\section{What is GPGPU}
		\section{Re-formulation of the algorithm for its Cg implementation}
		\section{CUDA implementation/optimisations \OC{ISBMS 2008a}}
		\section{Implementation into SOFA}
			\subsection{Presentation of SOFA project and architecture}
			\subsection{TLED in SOFA and release in open-source}

@@

	\chapter{State of art: hollow structures}
		\section{Expose the problem: models presented for solid organs are insufficient. How to model hollow organs?}
			\subsection{Colonoscopy simulator project: needs for colon}
			\subsection{Cataract surgery, stenosis: other needs for implants/blood vessels}
		\section{Non-physic approaches (computer graphics stuff)}
		\section{Physically accurate approches (plates/shells)}

	\chapter{Mass-spring model for colon implemented on GPU \OC{ISBMS 2008b}}
		\section{Colon is big, we need a fast model}
		\section{Limitations (difficult to link it to actual physical properties)}

	\chapter{A co-rotational triangular shell model \OC{ISBMS 2010}}
		\section{Model description}
		\section{Validation}
		\section{Application to implant deployment simulation in cataract surgery}

@@

\part{Conclusion}
	\chapter{Summary}
	\chapter{Discussion and perspectives (Interaction solid/hollow organs)}
